Supplemental Materials for the paper: \\Pesticides pollution of small streams in Germany

### 2016-08-10 article.tex
eqs model

\begin{align}
\begin{split}
  No_i \sim NB(\mu_i, k) \\
  E(No_i) = \mu_i~and~Var(No_i) = \mu_i + \frac{\mu_i^2}{k} \\
  log(\mu_i)= \beta_0 + f_1(Agri_i) + f_2(Size_i) + log(n_i)
\end{split}
\end{align}

where $No_i$ is the observed number of exceedances at site $i$, $Agri_i$ the proportion of agriculture within the catchment and $Size_i$ the catchment size of the site. 
We modeled $No_i$ as resulting from a negative binomial distribution ($NB$) and used the number of sampling events per site ($n_i$) as an offset to account different sampling efforts. 
$f_1$ and $f_2$ are smoothing functions using thin plate regression splines \citep{wood_thin_2003}.
The degree of smoothness was estimated using restricted maximum likelihood (REML) during model fitting process \citep{wood_fast_2011}.
Similar models were fitted to the number of EQS-exceedances and the 95th percentile of $TU_{max}$ (see Supplement). 
We used pointwise 95\% Confidence Intervals of the first derivative of the fitted smooth to check if there are regions of statistically significant changes.
GAMs were fitted using the mgcv package \citep{wood_fast_2011}.

@@

\begin{figure}
  \includegraphics[width=0.8\textwidth]{fig/figrac.pdf}
  \caption{Effect of agriculture within the catchment (left) and catchment size (right) on the number of RAC exceedances. Red line marks statistically significant increases. Dashed lines denote 95\% Confidence Intervals.
  }
  \label{fig:figrac}
\end{figure}

>>>>

\begin{align}
\begin{split}
  No_i \sim NB(\mu_i, k) \\
  E(No_i) = \mu_i~and~Var(No_i) = \mu_i + \frac{\mu_i^2}{k} \\
  log(\mu_i)= \beta_0 + f_1(Agri_i) + f_2(Size_i) + log(n_i)
\end{split}

\end{align}

where $No_i$ is the observed number of exceedances at site $i$, $Agri_i$ the proportion of agriculture within the catchment and $Size_i$ the catchment size of the site. 
We modeled $No_i$ as resulting from a negative binomial distribution ($NB$) and used the number of sampling events per site ($n_i$) as an offset to account different sampling efforts. 
$f_1$ and $f_2$ are smoothing functions using thin plate regression splines \citep{wood_thin_2003}.
The degree of smoothness was estimated using restricted maximum likelihood (REML) during model fitting process \citep{wood_fast_2011}.
Similar models were fitted to the number of EQS-exceedances and the 95th percentile of $TU_{max}$ (see Supplement for details). 
We used pointwise 95\% Confidence Intervals of the first derivative of the fitted smooth to check if there are regions of statistically significant changes.
GAMs were fitted using the mgcv package \citep{wood_fast_2011}.

@@

\begin{figure}
  \includegraphics[width=0.8\textwidth]{fig/figrac.pdf}
  \caption{Effect of agriculture within the catchment (left) and catchment size (right) on the number of RAC exceedances. Red line marks statistically significant changes. Dashed lines denote 95\% Confidence Intervals.
  }
  \label{fig:figrac}
\end{figure}

### 2016-08-10 supplement/Supplemental_Materials.tex
eqs model

@@

\begin{figure}[h]
	\centering
	\includegraphics[width = 0.75\textwidth]{precip}
	\caption{Distribution of precipitation at sampling occasions. top: at sampling date. bottom: at day before sampling.}
	\label{fig:precip}
\end{figure}

@@

With $y_i$ being $log(TU_{max~i})$ and $x_i$ the predictor functions $f_1(Agri_i) + f_2(Size_i)$. $P(censored|x_i)$ is the probability of censoring at given predictors. Further, we assumed constant variance. This model was fitted using the gamlss packages \citep{stasinopoulos_generalized_2007}.

\begin{figure}[h]
	\centering
	\includegraphics[width = 0.6\textwidth]{ezgagritu}
	\caption{Raw data of effect of agriculture and catchment size on the 95th percentile of log(TUmax).}
	\label{fig:ezgagritu}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width = 0.9\textwidth]{ezgagritumodel}
	\caption{Effect of agriculture within the catchment (left) and catchment size (rigth) on the 95th percentile of log(TUmax). The model took censored data into account (see description above). Dashed lines denote 95\% Confidence Intervals.}
	\label{fig:ezgagritu_model}
\end{figure}

>>>>

% Continuous figure counting (instead of per cahpter)
\usepackage{chngcntr}
\counterwithout{figure}{chapter}
\counterwithout{table}{chapter}
% Add 'S' before figure/table numbering
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thetable}{S\arabic{table}}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width = 0.6\textwidth]{precip}
	\caption{Distribution of precipitation at sampling occasions. top: at sampling date. bottom: at day before sampling.}
	\label{fig:precip}
\end{figure}

@@

With $y_i$ being $log(TU_{max~i})$ and $x_i$ the predictor functions $f_1(Agri_i) + f_2(Size_i)$. $P(censored|x_i)$ is the probability of censoring at given predictors. Further, we assumed constant variance. This model was fitted using the gamlss package \citep{stasinopoulos_generalized_2007}.

\begin{figure}[h]
	\centering
	\includegraphics[width = 0.6\textwidth]{ezgagritu}
	\caption{Raw data of effect of agriculture and catchment size on the 95th percentile of $log(TU_max)$.}
	\label{fig:ezgagritu}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width = 0.9\textwidth]{ezgagritumodel}
	\caption{Effect of agriculture within the catchment (left) and catchment size (rigth) on the 95th percentile of log(TUmax). The model took censored data into account (see description above). Dashed lines denote 95\% Confidence Intervals.}
	\label{fig:ezgagritumodel}
\end{figure}

\pagebreak
\section{EQS Exceedances}
We modeled the number of EQS exceedances (No) the same way as RAC exceedances (see main article).

\begin{figure}[h]
	\centering
	\includegraphics[width = 0.6\textwidth]{ezgagrieqs}
	\caption{Raw data used for modelling EQS exceedances. Color codes the number of EQS exceedances (on a log-scale). Grey points are sites without any exceedance.}
	\label{fig:ezgagrieqs}
\end{figure}

\begin{figure}
  \includegraphics[width=0.8\textwidth]{ezgagrieqsmodel}
  \caption{Effect of agriculture within the catchment (left) and catchment size (right) on the number of EQS exceedances. Red line marks statistically significant changes. Dashed lines denote 95\% Confidence Intervals.
  }
  \label{fig:ezgeqsagrimodel}
\end{figure}
